Difference-in-Differences with Spatial Spillover

### 2021-01-28 latex/slides/Spillover_slides.tex
Add Literature Review to Slides
For Research Methods 1 presentation

% Title ------------------------------------------------------------------------------
\title{Differnces-in-Differences with Spatial Spillover}
\date{\today}
\author{Kyle Butts}
% \institue{}

@@

    \begin{itemize}
        \item e.g. large employer opening/closing in a county have positive or negative employment effects on nearby counties
    \end{itemize}
\end{frame}

@@

        \item \textbf{Spillover onto other Treated Units:}

@@

    \begin{itemize}
        \item[1--] Using a potential outcomes framework, I derive the bias in the presence of spillovers

        \item[2--] Using Monte Carlo simulations, show when biases are large and analyze effectiveness of current adjustments done by applied researchers

@@

\begin{frame}{Preview of Results}
    There are two sources of bias:
        \begin{itemize}
            \item[1.] Treatment effects spillover onto control units
            \item[2.] Treatment effects spillover onto also treated units
        \end{itemize}

    Solutions:
        \begin{itemize}
            \item Fixing bias 1 is relatively easy and works better when you have relatively few treated units

            \item Bias 2 worsens as treatment locations bunch more (spatial correlation of treatment increases)

            \item However, spatial correlation of treatment decreases bias 1
        \end{itemize}
\end{frame}

@@

        \item \textbf{Average treatment among $k$-nearest neighbors:}

@@

\begin{frame}{Signing the Bias}
    \[ 
        \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}    
    \]

@@

    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 1$ if county $i$ shares a border with a treated county and $0$ otherwise.

@@

\begin{frame}{Partial Identification}
    Researchers can us the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.

    To formalize this, I follow the literature on partial identification for treatment effects:

    \begin{citecolor}
        [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
    \end{citecolor}
\end{frame}

>>>>

% Title ------------------------------------------------------------------------------
\title{Difference-in-Differences with Spatial Spillover}
\date{\today}
\author{Kyle Butts}
% \institue{}

@@

    \begin{itemize}
        \item e.g. large employer opening/closing in a county have positive employment effects on nearby counties
    \end{itemize}
\end{frame}

@@

        \vspace{2.5mm}
        \item \textbf{Spillover onto other Treated Units:}

@@

    \begin{itemize}
        \item[1--] Using a potential outcomes framework, I decompose the difference-in-differences estimator in to three parts:
        \begin{itemize}
            \item Direct Effect of Treatment
            \item Spillover onto Treated Units
            \item Spillover onto Control Units
        \end{itemize}

        \item[2--] Using Monte Carlo simulations:
        \begin{itemize}
            \item Show when biases are relatively large
            \item Analyze effectiveness of current adjustments done by applied researchers 
        \end{itemize}

@@

% @TODO: Literature Review
\begin{frame}{Contribution}

    \underline{Difference-in-Differences Estimation with Spillovers}

    \begin{citecolor}
        [\citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}]
    \end{citecolor}

    % \begin{itemize}
    %     \item My derivation generalizes the above papers by being in the form of potential outcomes.
    % \end{itemize}

    \underline{Potential Outcome Framework for Spillovers}

    \begin{citecolor}
        [\citet{Vazquez-Bare_2019}, \citet{Angelucci_DiMaro_2016}, \citet{Angrist_2014}]        
    \end{citecolor}

    \underline{Place-based Policies}

    \begin{citecolor}
        [\citet{Kline_Moretti_2014b} and \citet{Kline_Moretti_2014}]
    \end{citecolor}

    % \begin{itemize}
    %     \item I highlight the need to control for spillovers to properly estimate local effects of policies.
    % \end{itemize}
\end{frame}

@@

        \vspace{2.5mm}
        \item \textbf{Average treatment among $k$-nearest neighbors:}

@@

\begin{frame}{Biased Estimate for $\tau_{\text{direct}}$}
    \[ 
        \mathbb{E}[\hat{\tau}_{\text{diff-in-diff}}] - \textcolor{green}{\tau_{\text{direct}}} = \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}    
    \]

@@

    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) = 1$ if county $i$ shares a border with a treated county and $0$ otherwise.

@@

\begin{frame}{Partial Identification}
    Researchers can use the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.

    To formalize this, I follow the literature on partial identification for treatment effects
    \begin{citecolor}
        [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
    \end{citecolor}
\end{frame}
